---
title: "Developing Data Products"
author: "Atasie Diana"
date: "5/27/2019"
output: slidy_presentation
---

```{r , echo=FALSE}
library(knitr)
```

## General View

This is a part of a Coursera Assignment.The request is to have Reproducible Pitch Presentation and Shiny Application.

I used these packages for predict if a man or woman will be released or no.

You can find Shiny code on https://github.com/DianaAtasie/Assignment-Week.

## Dataset- Arrests from carData package

- released=Whether or not the arrestee was released with a summons; a factor with levels: No; Yes.
- colour=The arrestee's race; a factor with levels: Black; White.
- year=1997 through 2002; a numeric vector.
- age=in years; a numeric vector.
- sex=a factor with levels: Female; Male.
- employed=a factor with levels: No; Yes.
- citizen=a factor with levels: No; Yes.
- checks=Number of police data bases (of previous arrests, previous convictions, parole status, etc. – 6 in all) on which the arrestee's name appeared; a numeric vector

## Part of the data

```{r , echo = FALSE}
library(carData)
tail(Arrests)
```

## A view of released rate

```{r , echo=FALSE}
plot(Arrests$released)
```

